\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/experiment.tex
Update
Experiment

			\caption{Screen Mode Switch in Ubuntu.}

@@

\shuqing{May use statistics (instead of concrete examples) to explain it.}

@@

\subsubsection{Attack Scenario}

@@

To further test the capabilities of \tool in this attack scenario, we conducted a simulation experiment.
We selected 11 applications on \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
\ding{182} Login in with a test account.
\ding{183} Keep the default settings.
\ding{184} Attach attacker's \tool to the test device.
\ding{185} Simulate victim's daily usage of the application.

>>>>

			\caption{Switching Screen Mode in Ubuntu.}

@@

%\shuqing{May use statistics (instead of concrete examples) to explain it.}

@@

\subsubsection{Attack Scenario}
\label{subsec:attack-scenario}

@@

We conducted experiments to further validate the capabilities of \tool 
in the attack scenario introduced in Section~\ref{subsec:attack-scenario}.
11 applications were selected and tested on \mbox{\textit{HUAWEI P30 (ELE-AL00)}} step by step:
(1) Login in with a test account.
(2) Keep the default settings.
(3) Attach attacker's \tool to the test device.
(4) Simulate victim's daily usage of the application.
